Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-10-24 paper-correlations.tex
Fix a typo
New data for real samples

For surface-surface and surface-void functions we use an edge detection filter
and then calculate either autocorrelation of the edge or cross-correlation of
the edge and the void phase. The edge is extracted by convolving an input with a
short signal $E$ (\cref{eq:filter-1d} for 1D case, \cref{eq:filter-2d} for 2D case or
\cref{eq:filter-3d-1}-\cref{eq:filter-3d-3} for 3D case).
\begin{align}
  E^{1D} &= \frac{\sqrt{2}}{3} \left[
    \begin{array}{ccc}
        1 & -2 & 1
      \end{array}
    \right] \label{eq:filter-1d} \\
  E^{2D} &= \frac{\sqrt{2}}{9} \left[
    \begin{array}{ccc}
        1 & 1 & 1 \\
        1 & -8 & 1 \\
        1 & 1 & 1
      \end{array}
    \right] \label{eq:filter-2d} \\
  E^{3D}_{ij0} &= \frac{\sqrt{2}}{27} \left[
    \begin{array}{ccc}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3d-1} \\
  E^{3D}_{ij1} &= \frac{\sqrt{2}}{27} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -26 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3d-2} \\
  E^{3D}_{ij2} &= F^{3D}_{ij0} \label{eq:filter-3d-3}
\end{align}

@@

@@

\section{Examples and applications}
\label{sec:examples}
After the verification of our computational approach based on analytical
solution we can apply our algorithms to evaluate correlation functions for
different porous media images, including real XCT and SEM images.

For demonstration purposes, we computed correlation functions for images of
sandstone found on Digital Rocks Portal \cite{DigitalRocks} all of which have
dimensions $1000 \times 1000 \times 1000$. The result can be seen on
\cref{fig:real-data}.

\begin{figure*}[t]
  \centering
  \subfigure[$S_2^{(void)}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-s2void.png}
    \label{fig:real-s2}}
  \hfill
  \subfigure[$L_2^{(void)}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-l2void.png}
    \label{fig:real-l2}}
  \subfigure[$C_2^{(void)}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-c2void.png}
    \label{fig:real-c2}}
  \vskip\baselineskip
  \subfigure[$F_{ss}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-ss.png}
    \label{fig:real-ss}}
  \subfigure[$F_{sv}$ correlation function.]{
    \includegraphics[width=0.3\linewidth]{real-data-plots/real-sv.png}
    \label{fig:real-sv}}
  \caption[]{Plots of correlation functions for images of sandstones.}
  \label{fig:real-data}
\end{figure*}

>>>>

For surface-surface and surface-void functions we use an edge detection filter
and then calculate either autocorrelation of the edge or cross-correlation of
the edge and the void phase. The edge is extracted by convolving an input with a
short signal $E$ (\cref{eq:filter-1d} for 1D case, \cref{eq:filter-2d} for 2D case or
\cref{eq:filter-3d-1}-\cref{eq:filter-3d-3} for 3D case).
\begin{align}
  E^{1D} &= \frac{\sqrt{2}}{3} \left[
    \begin{array}{ccc}
        1 & -2 & 1
      \end{array}
    \right] \label{eq:filter-1d} \\
  E^{2D} &= \frac{\sqrt{2}}{9} \left[
    \begin{array}{ccc}
        1 & 1 & 1 \\
        1 & -8 & 1 \\
        1 & 1 & 1
      \end{array}
    \right] \label{eq:filter-2d} \\
  E^{3D}_{ij0} &= \frac{\sqrt{2}}{27} \left[
    \begin{array}{ccc}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3d-1} \\
  E^{3D}_{ij1} &= \frac{\sqrt{2}}{27} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -26 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3d-2} \\
  E^{3D}_{ij2} &= E^{3D}_{ij0} \label{eq:filter-3d-3}
\end{align}

@@

\section{Examples and applications}
\label{sec:examples}
After the verification of our computational approach based on analytical
solution we can apply our algorithms to evaluate correlation functions for
different porous media images, including real XCT and SEM images. A summary
which contains information about type of the images, dimensions and resolution
can be found in \cref{tab:samples}. XCT images of sandstones are provided by
Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of these samples
can be seen on \cref{fig:real-data}.

\begin{table*}[!pt]
  \centering
  \begin{ruledtabular}
    \begin{tabular}{|c|c|c|c|}
      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) \\
      \hline
      Bandera Brown sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Bentheimer sandstone    & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Kirby sandstone         & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 \\
      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 \\
      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06
    \end{tabular}
  \end{ruledtabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:samples}
\end{table*}

\begin{figure*}[pt]
  \centering
  \subfigure[Bandera Brown sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary.png}
    \label{fig:bandera}}
  \hfill
  \subfigure[Bentheimer sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary.png}
    \label{fig:bentheimer}}
  \hfill
  \subfigure[Kirby sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary.png}
    \label{fig:kirby}}
  \vskip\baselineskip
  \subfigure[Sandstone 1]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone1.png}
    \label{fig:real-sandstone-1}}
  \hfill
  \subfigure[Sandstone 2]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone2.png}
    \label{fig:real-sandstone-2}}
  \hfill
  \subfigure[Carbonate 1]{
    \includegraphics[width=0.3\linewidth]{real-data/carbonate1.png}
    \label{fig:real-carbonate-1}}
  \caption[]{Plots of correlation functions for real samples.}
  \label{fig:real-data}
\end{figure*}

@@
